Unsupervised embeddings capture latent structure of scientific mobility

### 2020-02-25 paper/current/main.tex
typo and the change umap part

%% Word2vec parameters and training procedure
The SGNS model has several tunable hyper-parameters, including the size of the learned vectors, the size of the token window  considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
We iterate through several values of vector size and window size, repeating analysis for each combination. 
To mitigate the effect of less common organizations, only organizations appearing at least 50 times in mobility sentences are included in the embedding;
this yields 6,580, or 76 percent of all organizations.
We iterate the SGNS training for five epochs over all mobility sentences. 
All word embeddings are trained using the \textit{gensim} python implementation of the SGNS \textit{word2vec} model. 
We visualize embeddings by projecting into two dimensions using UMAP~\cite{mcinnes2018umap}.

@@

We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{-\alpha}_{ij}$, where $\alpha$ is estimated from the data. 
For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data. 
To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_flux}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.

@@

%
% Figure - Conditional Probability
%
\begin{figure}
    \centering
    \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.png}
    \caption{Relationship between the conditional probability $p(j|i)$ and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
    \label{fig:real_embedding_relationship}
\end{figure}

@@

The SGNS model learns an effective distance from trajectories, one which we can visualize by projecting organizational vectors into two dimensions using UMAP \cite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
Overall, organizations are clustered by geography, according to the nations in which they are location;
however, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions at multiple scales.

>>>>

%% Word2vec parameters and training procedure
The SGNS model has several tunable hyper-parameters, including the size of the learned vectors, the size of the token window  considered when training, the minimum frequency threshold for including an organization, and the number of iterations.
We iterate through several values of vector size and window size, repeating analysis for each combination. 
To mitigate the effect of less common organizations, only organizations appearing at least 50 times in mobility sentences are included in the embedding;
this yields 6,580, or 76 percent of all organizations.
We iterate the SGNS training for five epochs over all mobility sentences. 
All word embeddings are trained using the \textit{gensim} python implementation of the SGNS \textit{word2vec} model.

@@

We consider separate variants of $f(r_{ij})$ for geographic distance, $g_{ij}$, and the embedding distance, $d_{ij}$, report the best-fit model of each distance.
For geographic distance, we use the power-law function of the gravity law, with $f(g_{ij})= g^{-\alpha}_{ij}$, where $\alpha$ is estimated from the data. 
For embedding distance , we use the exponential function, with $f(d_{ij}) = e^{-\beta d_{ij}}$, where $\beta$ is estimated from the data. 
To estimate parameters $\alpha$ and $\beta$ are estimated by log-transforming each variant of \ref{eq:gravity_basic}, obtaining Eq.~\ref{eq:linear_flux_geo} and Eq.~\ref{eq:linear_flux_emb} in the form of linear equations, and fitting parameters using linear regression.

@@

%
% Figure - Conditional Probability
%
\begin{figure}
    \centering
    \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.pdf}
    \caption{Relationship between the conditional probability $p(j|i)$ from data and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
    \label{fig:real_embedding_relationship}
\end{figure}

@@

The SGNS model learns an effective distance from trajectories, one which we can visualize the results into two dimensional space by projecting high dimensional organizational vectors into two dimensions vectors using UMAP \cite{mcinnes2018umap} (Fig.~\ref{fig:projection}a).
Overall, organizations are clustered by geography, according to the nations in which they are location;
however, the embedding space also reflects a mix of geographic, historic, cultural, and linguistic relationships between regions at multiple scales.
